Circumcision Paper Text

### 2024-04-14 paper/paper_cals.Rmd
Do many of section 5 calculationsvasjdlkfs

@@

```{r, echo = FALSE}
x1 <- readRDS("data/inlines/01_inlines.RDS")
for (i in seq_along(x1)) {
  assign(names(x1)[i], x1[[i]])
}
iso3_lowest_highest_cov <- simplify_type(iso3_lowest_highest_cov)
iso3_cov_diffs <- simplify_type(iso3_cov_diffs)
```

@@

```{r, echo = FALSE}
x2 <- readRDS("data/inlines/02_inlines.RDS")
for (i in seq_along(x2)) {
  assign(names(x2)[i], x2[[i]])
}
age_group_cov <- sapply(
  age_group_cov, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
age_group_cov_non_vmmc <- sapply(
  age_group_cov_non_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
age_group_cov_vmmc <- sapply(
  age_group_cov_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
```

@@

```{r}
# x5 <- readRDS("data/inlines/05_inlines.RDS")
# for (i in seq_along(x5)) {
#   assign(names(x5)[i], x5[[i]])
# }
# aggr_mean_circ_age <- tidy_age(aggr_mean_circ_age)
# aggr_mean_circ_age_non_vmmc <- tidy_age(aggr_mean_circ_age_non_vmmc)
# aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
```

@@

Amongst the 14 VMMC priority countries modelled, just 
x
 countries were projected to have achieved the VMMC target of 90\% MC coverage amongst 10-29 year olds, 
x
 and 
x
. 
MC coverage across these countries increased from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020.

x
 (
x
 to 
x
) circumcisions were performed between 2007 and 2020 in these countries. 
Of these, 
x
 (
x
 to 
x
) were MMCs. 
No countries were expected to have reached this goal in all districts. 
The number of annual MCs increased from 
x
 (
x
 to 
x
) in 2006 to 
x
 (
x
 to 
x
) in 2020.

x
 (
x
 to 
x
) additional circumcisions are required to achieve 90\% MC coverage in all VMMC countries, 
x
 (
x
 to 
x
) times the projected number of MCs for 2020. 
The largest increase in MC coverage amongst VMMC priority countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase.

>>>>

# recursively simplify type 
simplify_type_rec <- function(x) {
  # for e.g. vector
  if (!is.list(x)) {
    return(x)
  # simplify type in dataframes
  } else if (is.data.frame(x)) {
    if ("type" %in% names(x)) simplify_type(x)
  # traverse list
  } else simplify_type_rec(x[[1]])
  return(x)
}

@@

```{r, echo = FALSE}
x1 <- readRDS("data/inlines/01_inlines.RDS")
# x1 <- simplify_type_rec(x1)
for (i in seq_along(x1)) {
  assign(names(x1)[i], x1[[i]])
}
iso3_lowest_highest_cov <- simplify_type(iso3_lowest_highest_cov)
iso3_cov_diffs <- simplify_type(iso3_cov_diffs)
```

@@

```{r, echo = FALSE}
x2 <- readRDS("data/inlines/02_inlines.RDS")
# x2 <- simplify_type_rec(x2)
for (i in seq_along(x2)) {
  assign(names(x2)[i], x2[[i]])
}
age_group_cov <- sapply(
  age_group_cov, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
age_group_cov_non_vmmc <- sapply(
  age_group_cov_non_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
age_group_cov_vmmc <- sapply(
  age_group_cov_vmmc, simplify_type, simplify = FALSE, USE.NAMES = TRUE
)
```

@@

```{r}
x5 <- readRDS("data/inlines/05_inlines.RDS")
# x5 <- simplify_type_rec(x5)

for (i in seq_along(x5)) {
  assign(names(x5)[i], x5[[i]])
}

# aggr_mean_circ_age_vmmc <- tidy_age(aggr_mean_circ_age_vmmc)
n_required_vmmc       <- simplify_type(n_required_vmmc)
largest_smallest_vmmc <- simplify_type(largest_smallest_vmmc)
increase_vmmc         <- simplify_type(increase_vmmc)
cum_vmmc_circs_performed <- simplify_type(cum_vmmc_circs_performed)
vmmc_circs_performed <- simplify_type(vmmc_circs_performed)

# countries above threshold
cntries_thresh <- to_cntry_name(cntry_abv_thresh$iso3[cntry_abv_thresh$age_group == "15-49"])

@@

Amongst the 14 VMMC priority countries modelled, 
`r cntry_abv_thresh %>% filter(age_group == "15-49") %>% nrow()`
countries were projected to have achieved the VMMC target of 
80\% MC coverage amongst 15-49 year olds by 2020, 
`r paste(paste(cntries_thresh[-length(cntries_thresh)], collapse = ", "), last(cntries_thresh), sep = " and ")`.
None were expected to reach the 90\% target for 10-29 year olds. 
No countries were expected to have reached these goals in all districts.

MC coverage amongst 10-29 year olds across VMMC priority countries increased from 
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
) in 2006 to 
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
) in 2020, 
an increase of 
`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`
).
MMC coverage amongst 10-29 year olds across VMMC priority countries increased from 
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
) in 2006 to 
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_10_29$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
) in 2020, an increase of 
`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_10_29$cov_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`
).
MC coverage amongst 15-49 year olds across VMMC priority countries increased from 
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MC") %>% pull(upper) %>% to_percentage()`
) in 2006 to 
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MC") %>% pull(upper) %>% to_percentage()`
) in 2020, 
an increase of 
`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MC") %>% pull(upper) %>% to_percentage()`
).
MMC coverage amongst 15-49 year olds across VMMC priority countries increased from 
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2006, type == "MMC") %>% pull(upper) %>% to_percentage()`
) in 2006 to 
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_15_49$mean_cov %>% filter(year == 2020, type == "MMC") %>% pull(upper) %>% to_percentage()`
) in 2020, an increase of 
`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(mean) %>% to_percentage()`
`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(lower) %>% to_percentage()`
`r vmmc_cov_diff_15_49$cov_diff %>% filter(type == "MMC") %>% pull(upper) %>% to_percentage()`
).

Between 2006 and 2020 in these countries, 
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(mean) %>% to_mill()`
million
(
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(lower) %>% to_mill()`
million
-
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MC") %>% pull(upper) %>% to_mill()`
million
) MCs were performed on 10-29 year olds.
Of these, 
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
million
(
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
million
- 
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "MMC") %>% pull(upper) %>% to_mill()`
million
) were MMCs, and 
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
million
(
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
million
- 
`r cum_vmmc_circs_performed %>% filter(age_group == "10-29", type == "TMC") %>% pull(upper) %>% to_mill()`
million
) were TMCs. 
Over the same period, 
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(mean) %>% to_mill()`
million
(
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(lower) %>% to_mill()`
million
-
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MC") %>% pull(upper) %>% to_mill()`
million
) MCs were performed on 15-49 year olds,
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
million
(
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
million
- 
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "MMC") %>% pull(upper) %>% to_mill()`
million
) of which were MMCs, and 
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
million
(
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
million
- 
`r cum_vmmc_circs_performed %>% filter(age_group == "30-49", type == "TMC") %>% pull(upper) %>% to_mill()`
million
) of which were TMCs.

The number of annual MCs amongst 10-29 year olds increased from 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
million
) in 2006 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
million
) in 2020.

The number of annual MMCs amongst 10-29 increased from 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
million
) in 2006 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
million
) in 2020, while in constrast, the number of TMCs decreased from 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
million
) in 2006 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "10-29", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
million
) in 2020.

For 15-49 year olds, the number of annual MCs increased from 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MC") %>% pull(upper) %>% to_mill()`
million
) in 2006 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MC") %>% pull(upper) %>% to_mill()`
million
) in 2020.

Annual MMCs amongst 15-49 increased from 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "MMC") %>% pull(upper) %>% to_mill()`
million
) in 2006 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "MMC") %>% pull(upper) %>% to_mill()`
million
) in 2020, while in constrast, the number of TMCs decreased from 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2006, type == "TMC") %>% pull(upper) %>% to_mill()`
million
) in 2006 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(mean) %>% to_mill()`
million
 (
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(lower) %>% to_mill()`
million
 to 
`r vmmc_circs_performed %>% filter(age_group == "15-49", year == 2020, type == "TMC") %>% pull(upper) %>% to_mill()`
million
) in 2020.

`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean) %>% to_mill()`
 (
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower) %>% to_mill()`
 to 
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper) %>% to_mill()`
) additional circumcisions are required to achieve 90\% and 80\% MC coverage targets 
for 10-29 and 15-49 year olds, respectively, across all VMMC priority countries.

This equates to 
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff)`
(
`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
 to 
`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
)
and 
`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
(
`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
to
`n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
)
times the projected number of MCs for 10-29 and 15-49 year olds for 2020. 
The largest increase in MC coverage amongst VMMC priority countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase.
